Procurement Dynamics: Analyzing Federal Contract Awards to Microsoft

### 2024-11-26 paper/paper.qmd
Update Discussion

## Limitations of the Model

@@

>>>>

##

## Limitations

@@

## Next Steps

This paper provides a foundation for a deeper understanding of federal contract awards to Microsoft, but it also suggests several directions for future exploration. First, the study can expand to include comparisons with other major suppliers. By examining whether Microsoft's procurement trends are unique or reflective of broader patterns across industries. This gives a better understanding on assess whether certain dynamics are systemic within federal contracting practices.

Data quality and consistency issues are also of concern. The anomalies identified in this study, such as incomplete or inconsistent contract dates, highlight the need for improved data reporting standards. These discrepancies can be addressed in collaboration with government agencies to improve the reliability of procurement datasets and ensure that future analyses are more reliable and actionable.
